\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-04 paper.tex
10. Mental Health, Supreme Court

\subsubsection{``Public Good'' Breakdown}
I define the public good to be the population's mental and physical welfare. A healthy population is not addicted to World of Warcraft and therefore exhibits the ability to abstain from World of Warcraft, have unimpaired behavior control, and not crave playing World of Warcraft.

>>>>

\subsubsection{``Public Good'' Breakdown}
In 1996 the U.S. Supreme Court ruled that ``the mental health of the Nation's citizenry ... is a \emph{public good} of transcendent importance.'' \cite{SupremeCourtPublicGood} Addiction is a mental disease \cite{DefinitionOfAddiction} and therefore goes against the public good. A healthy population is not addicted to World of Warcraft and therefore exhibits the ability to abstain from World of Warcraft, have unimpaired behavior control, and not crave playing World of Warcraft.
